Automated data-driven symbolic modeling of the lift forces acting on flapping wings

### 2021-01-18 paper/main.tex
Update figure references

\subsection{Performance of models trained on one experiment versus many experiments}
Figure~\ref{fig:eq_goodbad}(A) illustrates the predictive performance of two models on data within their training sets, while Figure~\ref{fig:eq_goodbad}(B,C,D) illustrate the performance of those same two models on data outside their training sets. The differences between these two models result from the fact that one of them, $EQ_4$ from Table~\ref{table:eqmodels} (drawn in blue), was trained on 58 separate experiments simultaneously, whereas the other one, shown below (drawn in red), is one of many models trained only on the single experiment shown in Figure~\ref{fig:eq_goodbad}(A):
\begin{align}
 Force = \frac{C_1 + C_2\psi^2 - C_3\psi}{C_4 + \ddot{\theta} + C_5\dot{\theta} + \cos(C_6 -
  \frac{C_7}{\psi^2} - C_8\psi)} - C_9.
\label{eq:badeq}
\end{align}
Thus, $EQ_4$ shows strong qualitative and quantitative agreement with all of the experiments in Figure~\ref{fig:eq_goodbad}, indicating that this model is not over-fit but in fact generalizes well to new data. Equation~\eqref{eq:badeq}, on the other hand, fails to accurately predict the recorded data outside its training set.  Insufficient data and over-fitting are potential pitfalls of data-driven modeling, but are overcome in this case with a diverse sampling of training data.

>>>>

\subsection{Performance of models trained on one experiment versus many experiments}
Figure~\ref{fig:eq_goodbad_1} illustrates the predictive performance of two models on data within
their training sets, while Figures~\ref{fig:eq_goodbad_2},~\ref{fig:eq_goodbad_3},
and~\ref{fig:eq_goodbad_4} illustrate the performance of those same two models on data outside
their training sets. The differences between these two models result from the fact that one of them,
$EQ_4$ from Table~\ref{table:eqmodels} (drawn in blue), was trained on 58 separate experiments
simultaneously, whereas the other one, shown below (drawn in red), is one of many models trained
only on the single experiment shown in Figure~\ref{fig:eq_goodbad_1}:
\begin{align}
 Force = \frac{C_1 + C_2\psi^2 - C_3\psi}{C_4 + \ddot{\theta} + C_5\dot{\theta} + \cos(C_6 -
  \frac{C_7}{\psi^2} - C_8\psi)} - C_9.
\label{eq:badeq}
\end{align}
Thus, $EQ_4$ shows strong qualitative and quantitative agreement with all of the experiments in Figure~\ref{fig:eq_goodbad}, indicating that this model is not over-fit but in fact generalizes well to new data. Equation~\eqref{eq:badeq}, on the other hand, fails to accurately predict the recorded data outside its training set.  Insufficient data and over-fitting are potential pitfalls of data-driven modeling, but are overcome in this case with a diverse sampling of training data.
